Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

### 2021-09-21 Documents/Bookdown/03-ext-nhst.Rmd
add bookdown int analysis

Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest. That is the gender effect and the interaction between mother attachment and father attachment. Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_zinb)
```
Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_zinb)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects). Not that the marginal predicted values for gender are averaged over mother and father attachment effects. Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
```{r plot-nhst-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
```

>>>>

Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest. That is the gender effect and the interaction between mother attachment and father attachment. Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_zinb)
```
Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_zinb)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects-ext). Not that the marginal predicted values for gender are averaged over mother and father attachment effects. Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
```{r plot-nhst-effects-ext, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
```

### 2021-09-21 Documents/Bookdown/04-ext-model-comparison.Rmd
add bookdown int analysis

After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights).

```{r table-AIC-BIC-weights, cache=TRUE}
get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
                  BIC_weights = BIC_weights_ext,
                  problem = "ext",
                  format = params$format,
                  path_img = "images/")
```

@@

Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_mother)
```
Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_mother)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects). Not that the marginal predicted values for gender are averaged over mother attachment. Whereas, the marginal predicted values for mother attachment are averaged over gender.
```{r plot-comparison-effects, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_mother, attachment = "mother")
```

>>>>

After estimating the models, the AIC and BIC values together with their relative weights are computed. Results are reported in Table~\@ref(tab:table-AIC-BIC-weights-ext).

```{r table-AIC-BIC-weights-ext, cache=TRUE}
get_table_AIC_BIC(AIC_weights = AIC_weights_ext,
                  BIC_weights = BIC_weights_ext,
                  problem = "ext",
                  format = params$format,
                  path_img = "images/")
```

@@

Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_mother)
```
Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_mother)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects-ext). Not that the marginal predicted values for gender are averaged over mother attachment. Whereas, the marginal predicted values for mother attachment are averaged over gender.
```{r plot-comparison-effects-ext, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_mother, attachment = "mother")
```

### 2021-09-21 Documents/Bookdown/11-int-conclusion.Rmd
add bookdown int analysis

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Conclusions {#conclusion-ext}

Overall, we obtained consistent results from the three different approaches. Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems. In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems. Taken together, these results support the Monotropy Theory.

Although if the different approaches lead to apparently similar results, the rigorous interpretation of the results is very different.

- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect. Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses. 
- Only model comparison allow us to quantify the relative evidence of our models. Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment. However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects. Results clearly selected the Monotropy theory as the most likely theory among those considered.

To summarize, the apparently identical results actually have a completely different meaning and what we learn from the data is very different. Hopefully, now it is clear that statistical inference is a complex process that requires careful thinking. In particular, to answer the questions we are actually interested in, we need to apply the appropriate statistical techniques.

>>>>

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Conclusions {#conclusion-int}

Overall, we obtained consistent results from the three different approaches: only mother attachment influence children's externalizing problems. In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems. Compared to externalizing problems, however, difference between attachment groups are less pronounced. Taken together, these results support the Monotropy Theory.

### 2021-09-21 Documents/Bookdown/index.Rmd
add bookdown int analysis

In this section, the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems are presented following three different approaches.

@@

- **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented. The analyses follow the same structure as the case of externalizing problems. Thus, only differences will be highlighted.

>>>>

In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.

@@

In this section, we present the analyses evaluating the different role of mother attachment and father attachment on children's internalizing problems. We follow the three different approaches as for the externalizing problems analysis. This section is shorter than previous as we focus only on the results without repeating all the descriptions of the methods.

- **Chapter \@ref(model-choice-int) - Models Family Choice.**  We discuss the appropriate models family to to take into account data characteristics.
- **Chapter \@ref(nhst-int) - NHST.**  Analysis are conducted following the traditional Null Hypothesis Significance Testing (NHST).
- **Chapter \@ref(model-comparison-int) - Model Comparison.**  Analysis are conducted according to the  Model Comparison approach using the AIC and BIC criteria.
- **Chapter \@ref(BF-int) - Bayes Factor.**  Analysis are conducted following the Bayes Factor with encompassing prior approach.
- **Chapter \@ref(conclusion-int) - Conclusion.**  Results of the three approaches are discussed.
